---
title: "Comparing elpd_diff values for Hindi and Hindi-Kabardian"
author: "Amelia"
date: "16/08/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Parameters/ "degrees of freedom" affecting model results 
### Data Parameters
#### design
1. number of subjects: 30  
2. number of trials: 144 

#### data sampling/predictors: 
3. intercept = 1.3592 (based on pilots)
4. values: acoustic distances and Econ, Glob,Loc assigned based on design  
(https://docs.google.com/spreadsheets/d/1p-oHTYW3BOV3RMQPRBK8-JrQrIGJIOSUXm-C1fGeAk8/edit#gid=1153981776) 
    + acoustic distances include jitter for each instance of a phone; Econ, Glob, Loc do not
5. coefficients:  
    + data sampled based on Econ, Glob,Loc each given coef of -1,0,1
    + coef of acoustic distance based on pilots: -.1784

6. Number of datasets =1 (this document compares only one instance of each dataset,
but pipeline includes tools to sample multiple)

### Model Parameters
7. iterations: 2000
8. chains: 4
9. positive constrained priors:
    + normal(0,10), truncated at 0 by specifying <lower=0>
10. parameters of the horseshoe prior, appled to negative constrained priors:  
    + real<lower=0> scale_global;   // scale for the half-t prior for tau
    + real<lower=1> nu_global;      // degrees of freedom for the half-t prior for tau
    + real<lower=0> nu_local;        // degrees of freedom for the half-t prior for lambdas
    + real<lower=0> slab_scale;      // slab scale for the regularized horseshoe
    + real<lower=0> slab_df;        // slab degrees of freedom for the regularized horseshoe





### overall elpd_diff / se_diff

```{r overall_diffs, echo=FALSE, message=FALSE}
`%>%`<-magrittr::`%>%`
hindi_loo_diff <-readr::read_csv("loo_diffs_hindi_dinst2_Sept_2.csv")
hk_loo_diff<-readr::read_csv("loo_diffs_hk_dinst1_Sept_2.csv")

all_loo_diffs<-dplyr::full_join(hindi_loo_diff,hk_loo_diff) %>%
               dplyr::filter(!is.na(elpd_diff))

all_loo_diffs$elpd_over_se <-NA
for (i in 1:nrow(all_loo_diffs)){
  all_loo_diffs$elpd_over_se[i] <- all_loo_diffs$elpd_diff[i]/all_loo_diffs$se_diff[i]
}

#identify outliers in se_diff
loo_diffs_outliers<-subset(all_loo_diffs, all_loo_diffs$se_diff > 20)

all_loo_diffs<-subset(all_loo_diffs, all_loo_diffs$se_diff < 20)

library(ggplot2)
ggplot(all_loo_diffs, aes(elpd_over_se, fill = d_experiment)) +
  geom_histogram()

ggplot(all_loo_diffs, aes(elpd_diff, fill = d_experiment)) +
  geom_histogram()

ggplot(all_loo_diffs, aes(se_diff, fill = d_experiment)) +
  geom_histogram()


```

<!-- ### elpd_diff based on number of coeffs values that matching the model used -->
<!-- (prediction: more matching coeffs, smaller elpd_diffs ) -->

<!-- ```{r, echo=FALSE} -->

<!-- ggplot(all_loo_diffs, aes(x=as.factor(NUM_MATCHES), y=elpd_diff)) + -->
<!--   geom_violin() + -->
<!--   xlab("Number of coefficients for which the model matches the sign of the coeff as sampled") -->
<!-- ``` -->

<!-- ### se_diff based on number of coeffs values that matching the model used -->

<!-- ```{r, echo=FALSE} -->
<!-- ggplot(all_loo_diffs, aes(x=as.factor(NUM_MATCHES), y=se_diff)) + -->
<!--   geom_violin() + -->
<!--   xlab("Number of coefficients for which the model matches the sign of the coeff as sampled") -->

<!-- ``` -->

<!-- ### elpd_diff based on number of zero coeffs sampled -->

<!-- ```{r, echo=FALSE} -->
<!-- #calculate number of zeros  -->

<!--  LOO_DIFF_FILE$num_zeroes <-dplyr::case_when( -->
<!--      LOO_DIFF_FILE$d_coef_econ == 0 & LOO_DIFF_FILE$d_coef_loc == 0 & LOO_DIFF_FILE$d_coef_glob == 0 ~ "three", -->
<!--      LOO_DIFF_FILE$d_coef_econ!= 0 & LOO_DIFF_FILE$d_coef_loc == 0 & LOO_DIFF_FILE$d_coef_glob == 0 ~ "two", -->
<!--      LOO_DIFF_FILE$d_coef_econ == 0 & LOO_DIFF_FILE$d_coef_loc != 0 & LOO_DIFF_FILE$d_coef_glob == 0 ~ "two", -->
<!--      LOO_DIFF_FILE$d_coef_econ == 0 & LOO_DIFF_FILE$d_coef_loc == 0 & LOO_DIFF_FILE$d_coef_glob != 0 ~ "two", -->
<!--      LOO_DIFF_FILE$d_coef_econ != 0 & LOO_DIFF_FILE$d_coef_loc != 0 & LOO_DIFF_FILE$d_coef_glob == 0 ~ "one", -->
<!--      LOO_DIFF_FILE$d_coef_econ == 0 & LOO_DIFF_FILE$d_coef_loc != 0 & LOO_DIFF_FILE$d_coef_glob != 0 ~ "one", -->
<!--      LOO_DIFF_FILE$d_coef_econ != 0 & LOO_DIFF_FILE$d_coef_loc == 0 & LOO_DIFF_FILE$d_coef_glob != 0 ~ "one", -->
<!--      LOO_DIFF_FILE$d_coef_econ != 0 & LOO_DIFF_FILE$d_coef_loc !=0 & LOO_DIFF_FILE$d_coef_glob != 0 ~ "zero") -->

<!-- ggplot(LOO_DIFF_FILE, aes(x=num_zeroes, y=elpd_diff)) + -->
<!--   geom_violin() + -->
<!--   xlab("Number of coefficients sampled based on a zero effect")+ -->
<!--   scale_x_discrete(limits=c("zero","one","two","three"))  -->


<!-- ``` -->

<!-- ### se_diff based on number of zero coeffs sampled -->

<!-- ```{r, echo=FALSE} -->
<!-- ggplot(all_loo_diffs aes(x=num_zeroes, y=se_diff)) + -->
<!--   geom_violin() + -->
<!--   xlab("Number of coefficients sampled based on a zero effect")+ -->
<!--   scale_x_discrete(limits=c("zero","one","two","three")) -->
<!-- ``` -->

