---
title: "Correct Model Checking"
author: "Amelia"
date: "27/09/2019"
output:
  pdf_document: default
  html_document: default
---
This document takes as inputs the "final_corr_master" files created by 
"build_corr_masters.R"
```{r read in data, warnings = FALSE, message = FALSE,echo=FALSE}

hindi_dinst1<-readr::read_csv("final_corr_master_hindi_dinst1.csv")
  hindi_dinst1$numsubjs<-30
hindi_dinst2<-readr::read_csv("final_corr_master_hindi_dinst2.csv")
  hindi_dinst2$numsubjs<-30
hindi_dinst3<-readr::read_csv("final_corr_master_hindi_dinst3.csv")
  hindi_dinst3$numsubjs<-60
hindi_dinst4<-readr::read_csv("final_corr_master_hindi_dinst4.csv")
  hindi_dinst4$numsubjs <- 90
hindi_dinst5<-readr::read_csv("final_corr_master_hindi_dinst5.csv")
  hindi_dinst5$numsubjs<- 10
#hindi_dinst6<-readr::read_csv("corr_master_hindi_dinst6.csv")
#  hindi_dinst6$numsubjs<- 1000
#skipping dinst6 because brmses not done running 

  #skipping 1 so that have equal numbers of each 
hindi_for_hists<-dplyr::bind_rows(hindi_dinst2,
                                  hindi_dinst3,
                                  hindi_dinst4,
                                  hindi_dinst5) 

fake_grid_dinst1<-readr::read_csv("corr_master_fake_grid_dinst1.csv")
    fake_grid_dinst1$numsubjs  <-30
fake_grid_dinst2<-readr::read_csv("corr_master_fake_grid_dinst2.csv")
    fake_grid_dinst2$numsubjs  <-60
fake_grid_dinst3<-readr::read_csv("corr_master_fake_grid_dinst3.csv")
    fake_grid_dinst3$numsubjs  <-90
fake_grid_dinst4<-readr::read_csv("corr_master_fake_grid_dinst4.csv")
    fake_grid_dinst4$numsubjs <- 10
fake_grid_dinst5<-readr::read_csv("corr_master_fake_grid_dinst5.csv")
    fake_grid_dinst5$numsubjs <- 1000

fake_grid_for_hists<-dplyr::bind_rows(fake_grid_dinst1,
                                      fake_grid_dinst2,
                                      fake_grid_dinst3,
                                      fake_grid_dinst4,
                                      fake_grid_dinst5)


```

vizualise the coef differences calculated by glms 

```{r glm diffs, echo=FALSE}

ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Econ_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Econ coef differenece,hindi data,
                                        calculated by glm, by number of subjects")+
    ggplot2::facet_grid(numsubjs ~ .)


ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Glob_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Glob coef differenece, hindi data,
                     calculated by glm, by number of subjects")+
    ggplot2::facet_grid(numsubjs ~ .)


ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Loc_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Loc coef differenece, hindi data,
                                 calculated by glm, by number of subjects")+
    ggplot2::facet_grid(numsubjs ~ .)



ggplot2::ggplot(fake_grid_for_hists, ggplot2::aes(x = Econ_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Econ coef differenece,fake grid data,
                     calculated by glm, by number of subjects")+
    ggplot2::facet_grid(numsubjs ~ .)


ggplot2::ggplot(fake_grid_for_hists, ggplot2::aes(x = Glob_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Glob coef differenece, fake grid data,
                     calculated by glm, by number of subjects")+
    ggplot2::facet_grid(numsubjs ~ .)


ggplot2::ggplot(fake_grid_for_hists, ggplot2::aes(x = Loc_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Loc coef differenece, fake grid data,
                     calculated by glm, by number of subjects")+
    ggplot2::facet_grid(numsubjs ~ .)


```

##variability in posterior draws for hindi model 
these graphs show the sd for each of the 27 correct models for
each of the four data instances for hindi

plots faceted by number of subjects/data instance

```{r brms_plots_hindi, echo=FALSE}
ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = econ_sd)) +
  ggplot2::geom_histogram(binwidth = .1,position="identity", alpha = 0.4)+
  ggplot2::scale_x_continuous(limits = c(0,2))+
  ggplot2::ggtitle("sds of econ posterior")+
  ggplot2::facet_grid(numsubjs ~ .)

ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = glob_sd)) +
  ggplot2::geom_histogram(binwidth = .1,position="identity", alpha = 0.4)+
  ggplot2::scale_x_continuous(limits = c(0,2))+
  ggplot2::ggtitle("sds of glob posterior")+
  ggplot2::facet_grid(numsubjs ~ .)

ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = econ_sd)) +
  ggplot2::geom_histogram(binwidth = .1,position="identity", alpha = 0.4)+
  ggplot2::scale_x_continuous(limits = c(0,2))+
  ggplot2::ggtitle("sds of loc posterior")+
  ggplot2::facet_grid(numsubjs ~ .)

```

rhats for hindi models -- 

```{r brms_hindi_rhats, echo=FALSE}
ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Econ_brms_rhat)) +
  ggplot2::geom_histogram(binwidth = .1,position="identity", alpha = 0.4)+
  ggplot2::scale_x_continuous(limits = c(0,2))+
  ggplot2::ggtitle("rhats of econ")+
  ggplot2::facet_grid(numsubjs ~ .)

ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Glob_brms_rhat)) +
  ggplot2::geom_histogram(binwidth = .1,position="identity", alpha = 0.4)+
  ggplot2::scale_x_continuous(limits = c(0,2))+
  ggplot2::ggtitle("rhats glob")+
  ggplot2::facet_grid(numsubjs ~ .)

ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Loc_brms_rhat)) +
  ggplot2::geom_histogram(binwidth = .1,position="identity", alpha = 0.4)+
  ggplot2::scale_x_continuous(limits = c(0,2))+
  ggplot2::ggtitle("rhats  loc")+
  ggplot2::facet_grid(numsubjs ~ .)

```
